---
title: "Statistical Inference part 1"
author: "Mike"
date: "2023-04-03"
output: html_document
---

# Overview

In this report, I will be investigating the exponential distribution in R and 
compare it with the Central Limit Theorem (CLT). I will be investigating the distribution of averages of 40 exponentials, and a total of a thousand simulations. 

### What is exponential distribution?
From Wikipedia: Exponential distribution describes times between events happening at constant rate lambda with expected value 1/lambda.

In summary, this report will 
1. Show the sample mean and compare it to the theoretical mean of the distribution
2. Show how variable the sample is (via variance) and compare it to the theoretical
variance of the distribution
3. Show that the distribution is approximately normal

# Simulation

The exponential distribution is simulated with `rexp(n, lambda)`, where lambda is the rate parameter. The mean of exponential distribution and standard deviation is 1/lambda. Lambda is set at 0.2 for all simulations.

### Sample exponential distribution
```{r}
set.seed(666) # to make result reproducible
nosim <- 1000 # no of simulations
n <- 40 # no of exponentials
lambda <- 0.2 # rate parameter 
simdata <- matrix(rexp(nosim * n, rate=lambda), nosim)
sim_mean <- rowMeans(simdata) # row means
# calculate mean, sd and variance of sample exp dist
simdata_mean <- mean(sim_mean)
simdata_sd <- sd(sim_mean)
simdata_var <- var(sim_mean)
```

Now let's generate a theoretical distribution.
### Theoretical exponential distribution
```{r}
# calculate mean, df and variance of theoretical exp dist
t_mean = 1/lambda
t_sd = (1/lambda) * (1/sqrt(n))
t_var = t_sd^2
```


# Histogram of sample exponential distribution vs Averages of simulated exponentials.

```{r plot 1, echo=FALSE}
par(mfrow = c(1, 2))
hist(simdata,
     main = "Simulated exponential distribution",
     xlab = "40 random exponentials")
hist(sim_mean,
     main = "Averages of Simulated Exponentials",
     xlab = "Average of 40 exponentials")
abline(v = t_mean, col = "green", lwd = 2) # theoretical mean
```

The left histogram shows the simulated exponential distribution
The right histogram shows the averages of simulated exponentials. Shape is close to the normal distribution. 
The green line represents the theoretical mean of the distribution. MA of simulated distribution is closed to the line.

#Comparison between sample and theoretical statistics

```{r Table 1, echo=FALSE}
Sample_stats <- c(simdata_mean, simdata_sd, simdata_var)
Theoretical_stats <- c(t_mean, t_sd, t_var)
diff <-
  c(abs(t_mean - simdata_mean),
    abs(t_sd - simdata_sd),
    t_var - simdata_var)
names <- c("Mean", "Std", "Variance")
data.frame(Sample_stats,
           Theoretical_stats,
           diff,
           row.names =  c("Mean", "Std", "Variance"))
```

The difference between sample mean and theoretical mean and sample is 0.012

#Distribution

```{r plot 2, echo=FALSE}
library(ggplot2)
simdata_mean <- data.frame(sim_mean)
ggplot(simdata_mean, aes(sim_mean)) +
    geom_histogram(
        binwidth = .3,
        fill = "steelblue",
        color = "black",
        aes(y = ..density..)
    ) +
    geom_density(color = "blue", lwd = 1) +
    labs(title = "Distribution of Random Exponential Values with 1000 simulations",
         x = "Average of 40 Exponentials", y = "Density") +
    stat_function(
        fun = dnorm,
        args = list(mean = t_mean, sd = t_sd),
        color = "red",
        lwd = 1
    ) +
    theme_bw()
```

The red line is the theoretical normal distribution density, whereas the blue line is the density of the sample distribution. We can see that the sample distribution is close to normal

```{r plot 3, echo=FALSE}
qqnorm(sim_mean, col="black") # sample distribution
qqline(sim_mean, col="red", lwd=3) #theoretical
```

Observing the normal Q-Q plot, we can conclude that the sample distribution approximates the theoretical normal distribution quite closely, with the tails being less normal.


Based on the comparisons and the plots, the simulated sample distribution (as n grows larger) does indeed have similar means and variance with the theoretical distribution. This proves the Central Limit Theorem is correct. 