**Load the data**
```{r}
library(ggplot2)
data(ToothGrowth)
```

*1. Summary of the data*

**Take a look what is inside**
```{r}
head(ToothGrowth)
```

**Type of Supplements and Dosages**
```{r}
table(ToothGrowth$supp) # Supplement
table(ToothGrowth$dose) # Dosage
```

**Summary of ToothGrowth**
```{r}
summary(ToothGrowth)
```

**Correlation in ToothGrowth data**
```{r}
cor(ToothGrowth[sapply(ToothGrowth, is.numeric)])
```

We can see that the length of the tooth and the dosage have a high correlation

**Plotting**
```{r}
p1 <- ggplot(ToothGrowth, aes(x =factor(dose), y = len, fill = factor(dose)))
p1 + geom_boxplot() + xlab("Dosage") + ylab("Length")
```

Again, the boxplot shows more clearly that as the dosage increases, the length of the tooth increases.

*2. Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose*

**The 95% Confidence Intervals of Tooth Grow**
```{r}
Interval <- (mean(ToothGrowth$len) + c(-1, 1) * qnorm(0.975) * sd(ToothGrowth$len)/sqrt(length(ToothGrowth$len)))
Interval
```

**T-Test by length and Supplements**
```{r}
t.test(len~supp, data=ToothGrowth)
```

This T-Test shows that we cannot reject the Null hypothesis.

**T-Test of Dosage Level**

Subset Data
```{r}
dos1 <- subset(ToothGrowth, dose == 0.5)
dos2 <- subset(ToothGrowth, dose == 1)
dos3 <- subset(ToothGrowth, dose == 2)
```

T-Test
```{r}
t.test(len~supp, data=dos1) # Small Dosage = 0.5
t.test(len~supp, data=dos2) # Medium Dosage = 1
t.test(len~supp, data=dos3) # Big Dosage = 2
```

- For Small and Medium dosage, their p-values are small, so we can reject the null hypothesis
- For Big Dosage, we cannot reject the null hypothesis

*3. State your conclusions and the assumptions needed for your conclusions*

- The Tooth Length Growth is not controlled by Supplements.
- For dosage level 0.5 and 1, the Orange Juice has a higher effect on the length of tooth of Guinea Pigs than the Vitamin C.
- For dosage level 2, there are so such difference between Orange Juice and Vitamin C